\documentclass{article}

% \usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{xcolor}
    \usepackage[T1]{fontenc}
    % \usepackage{helvet}
    % \renewcommand{\rmdefault}{phv}
    % \renewcommand{\sfdefault}{phv}
    \renewcommand{\rmdefault}{cmss}
    \renewcommand{\sfdefault}{cmss}
    % cmss
    
    \usepackage{fancyhdr}
    \usepackage{lastpage}
    \pagestyle{fancy}
    \fancyhf{}
    
    \fancyfoot[L]{Last updated: 31 October 2023} %% NOTE:
    % don't forget to update the date on the other pages
    \fancyfoot[R]{Page \thepage\ of \pageref{LastPage}}
    \chead{Evan Habbershaw}
    \renewcommand{\footrulewidth}{0.1pt}
    \renewcommand{\headrulewidth}{0.1pt}
    
\fancypagestyle{firstpage}{
    \fancyhf{} % Clear all header and footer fields
    \fancyfoot[L]{Last updated: 20 October 2023} %% NOTE:
    % don't forget to update the date on the other pages
    \fancyfoot[R]{Page \thepage\ of \pageref{LastPage}} % Footer for the first page
    \renewcommand{\footrulewidth}{0.1pt}
    \renewcommand{\headrulewidth}{0pt}
}

% \fancypagestyle{others}{
%   \fancyhf{} % Clear all header and footer fields
%   \renewcommand{\headrulewidth}{1pt} % Remove the header line
%   \renewcommand{\footrulewidth}{1pt} % Remove the footer line
%   \fancyfoot[R]{Page \thepage\ of \pageref{LastPage}} % Footer for other pages
  
%     \fancyfoot[L]{Last updated: \today}
%     \fancyfoot[R]{Page \thepage\ of \pageref{LastPage}}
%     \chead{Evan Habbershaw}
% }


\begin{document}
\thispagestyle{firstpage}
\begin{center}
    % \thispagestyle{empty}
    \huge \textbf{Evan Habbershaw\\}
    \normalsize Curriculum Vitae \\ \texttt{ehabbers@vols.utk.edu}% $\mid$ 
    \\
    \hrulefill
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\noindent \textbf{\underline{OBJECTIVE}} \\
%\noindent Graduate Teaching Associate applying for the Upper School Math Instructor position at the Webb School of Knoxville. \\

\begin{center}
    \textbf{\underline{EDUCATION}}
\end{center}

\noindent \textbf{University of Tennessee, Knoxville}
  \hfill Knoxville, TN
\\
\textit{PhD, Mathematics}
  \hfill 2018-present
\\
\textit{Thesis: Numerical Methods for Multi-Species BGK Models}
\\
\\
\textbf{California State University, Northridge}
  \hfill Northridge, CA
\\
\textit{MS, Applied Mathematics}
  \hfill 2015-2018
\\
\textit{Thesis: Modeling the Impact of Host-Vector Interactions on Pathogen Transmission Between Hosts}
\\
\\
\textbf{California State University, Northridge}
  \hfill Northridge, CA
\\
\textit{BS, Mathematics}
  \hfill 2010-2015

  
\begin{center}
    \textbf{\underline{RESEARCH EXPERIENCE}}
\end{center}

\noindent \textbf{University of Washington, Steattle}
  \hfill Seattle, WA
\\
\textit{Visiting Scholar (planned visit)}
  \hfill January $-$ March 2024
\\
Project: \textit{Positivity Preserving Schemes for Multispecies BGK Models \& Multispecies Fokker-Planck (Lenard-Bernstein) Models}
\\
  Advisors: Jingwei Hu and Cory Hauck
\\
\\
\noindent \textbf{Oak Ridge National Laboratory}
  \hfill Oak Ridge, TN
\\
\textit{Graduate Research Associate}
  \hfill January 2022 $-$ July 2024
\\
Project: \textit{BGK Kinetic Equations (ORNL-DOE-UT-Battelle CW24420)}
\\
  Advisors: Cory Hauck and Steven Wise
\\
\\
\textit{Graduate Research Associate}
  \hfill June 2020 $-$ June 2021
\\
Project: \textit{Developing a Better Understanding of
Adaptive Velocity Grids for Kinetic Equations (LANL-ORNL-DOE-UT-Battelle RFP584197)}
\\
Advisors: Cory Hauck, Steve Wise, and Jeffrey Haack
\\
\\
\textbf{California State University, Northridge}
  \hfill Northridge, CA
\\
\textit{Master's Thesis Research}
  \hfill August 2016 $-$ July 2018
\\
Project: \textit{Modelling vector-borne plant diseases: Build and analyze a model that incorporates the effects of vector-induced defensive host responses and investigate stability}
% Project: \textit{Modeling the Impact of Host-Vector Interactions on Pathogen Transmission Between Hosts}
\\
Advisor: Jing Li
\\
\\
\textbf{The Ohio State University, Mathematical Biosciences Institute}
  \hfill Columbus, OH
\\
\textit{US-Canadian Epidemiology Summer School: Mathematical Modeling of Infectious Disease Spread} 
  \hfill June 2016
\\
Project: \textit{Investigating disease dynamics of Zika and Dengue on a single population; Can Zika virus invade a system where Dengue is endemically present?}
\\
Advisor: Joseph Tien

\begin{center}
    \textbf{\underline{PUBLICATIONS}}
\end{center}

\begin{etaremune}
    \item E. Habbershaw, C.D. Hauck, and S.M. Wise, \textit{Implicit Euler Step of Moment Equations for a Multi-Species, Homogeneous BGK Model}. (Manuscript in preparation.)
    
    \item E. Habbershaw, R.S. Glasby, J.R. Haack, C.D. Hauck, and S.M. Wise, \textit{Asymptotic Relaxation of Moment Equations for a Multi-Species, Homogeneous BGK model}. SIAM J. Appl. Math. (in review).
    \\
    Preprint at https://arxiv.org/abs/2310.12885
    
    \item E. Habbershaw and S.M. Wise, \textit{A Progress Report on Numerical Methods for BGK-Type Kinetic Equations}.
    TRACE: Faculty Publications and Other Works, Mathematics, The University of Tennessee (2022) Report number 10.
    \\
    \texttt{https://trace.tennessee.edu/utk\textunderscore mathpubs/10/}
    
    \item E. Habbershaw, \textit{Modeling the Impact of Host-Vector Interactions on Pathogen Transmission Between Hosts}.
    CSUN ScholarWorks Open Access Repository (2018).
    \\
    \texttt{http://hdl.handle.net/10211.3/205734}
\end{etaremune}

% \thispagestyle{others}

\begin{center}
    \textbf{\underline{TEACHING EXPERIENCE}}
\end{center}
\textbf{University of Tennessee, Knoxville}
  \hfill Knoxville, TN
\\
\textit{Graduate Teaching Associate, Department of Mathematics}
  \hfill Jan. 2019 $-$ May 2020 \& Aug. $-$ Dec. 2021
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Taught several classes in hybrid/flipped format
    \item Courses Taught:
        \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
            \item Co-taught large section of MATH 119 (College Algebra, 40+ students, Spring 2019)
            \item Instructor of record for MATH 119 (1 section) and MATH 125 (2 sections) (approximately 25 students each)
            \item Co-taught extra large online section of MATH 125 (Basic Calculus, 360 students, Fall 2021)
        \end{itemize}
    \item Main duties:
        \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
            \item In class: Presented lectures / in-class instruction, facilitated group work, encouraged collaboration.
            \item Out of class: Promptly graded and provided useful feedback on all assignments, held office hours to individually assist students, promptly responded to student emails, maintained gradebook, proctored and graded midterm and final exams. \\
            % \item Presented lectures / in-class instruction
            % \item Facilitated group work and encouraged collaboration
            % \item Graded assignments promptly and provided useful feedback on all class materials (homework, worksheets, exams)
            % \item Maintained gradebook
            % \item Held office hours to individually assist students
            % \item Promptly responded to student emails
            % \item Proctored common midterm and final exams 
            % \item Graded common midterm and final exams \\
        \end{itemize}
\end{itemize}

\noindent \textbf{California State University, Northridge}
  \hfill Northridge, CA \\
\textit{Graduate Teaching Associate, Department of Mathematics and Statistics} \hfill August 2015 $-$ May 2018
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Courses Taught over the course of the appointment:
        \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
            \item Instructor of record for 5 sections of \textit{Mathematical Ideas} (MATH 131)
            \item Recitation Instructor for the following
            \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
                \item \textit{College Algebra} (MATH 102L): 5 sections
                \item \textit{Business Calculus} (MATH 103L): 9 sections
                \item \textit{Precalculus} (MATH 105L): 2 sections
                \item \textit{Calculus I} (MATH 150AL): 1 section
                \item \textit{Calculus II} (MATH 150BL): 3 sections
                \item \textit{Calculus for the Life Sciences I} (MATH 255AL): 1 section
                \item \textit{Calculus for the Life Sciences II} (MATH 255BL): 1 section
            \end{itemize}
        \end{itemize}
    \item Main duties:
        \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
            \item Helped design MATH 131 course materials; worked with students on projects incorporating mathematics into their major.
            \item In class: Presented lectures / in-class instruction, facilitated group work, encouraged collaboration.
            \item Out of class: Promptly graded and provided useful feedback on all assignments, held office hours to individually assist students, promptly responded to student emails, maintained gradebook, proctored and graded midterm and final exams. \\
            % \item Presented lectures / in-class instruction
            % \item Facilitated group work and encouraged collaboration
            % \item Graded assignments promptly and provided useful feedback on all class materials (homework, worksheets, exams)
            % \item Maintained gradebook
            % \item Held office hours to individually assist students
            % \item Promptly responded to student emails
            % \item Proctored common midterm and final exams 
            % \item Graded common midterm and final exams \\
        \end{itemize}
\end{itemize}

\noindent \textit{Mathematics Tutor, Mathematics Department Tutoring Center}
  \hfill August 2013 $-$ May 2015
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Provided tutoring for all 100 and 200 level mathematics courses (including Calculus III and Differential Equations), and various 300 and 400 level courses
\end{itemize}

\begin{center}
    \textbf{\underline{SCHOLARSHIPS AND AWARDS}}% AND HONORS}}
\end{center}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Mathematics Department Graduate Research Associateship, UTK Mathematics Department (dates above)
    \item Mathematics Department Graduate Teaching Associateship, UTK Mathematics Department (dates above)
    \item Edgar and Dorothea Eaves Graduate Teaching Assistant Award Nominee (May 2020)
    \item Mathematics Department Outstanding Graduate Student Award (May 2018) (\$500 Cash Prize)
    \item Mathematics Department Outstanding Teaching Associate Award (May 2018) (\$500 Cash Prize)
    \item DataJam Data Science Competition (Fall 2017) - Best Use of Reproducible Research (\$1,000 Cash Prize)
    \item Mathematics Department Graduate Teaching Associateship, CSUN Mathematics Department (August 2015 - May 2018)
\end{itemize}

% \clearpage
\begin{center}
    \textbf{\underline{RESEARCH PRESENTATIONS}}
\end{center}
\begin{etaremune}
    \item \textit{Numerical Methods for BGK Kinetic Models}
    \\
    Mathematics in Computation Series, Oak Ridge National Laboratory, Oak Ridge, TN. November 2023 (planned).
    
    \item \textit{Asymptotic Relaxation and Implicit Euler Methods for a Multispecies BGK Models}
    \\
    Computational and Applied Mathematics Seminar, University of Tennessee, Knoxville, TN. 24 October 2023.

    \item \textit{BGK Models: Single Species and Multispecies}
    \\
    Series of 2 talks for Graduate Presentation Seminar,
    % \textcolor{blue}{(Include? Or is this padding)}
    University of Tennessee, Knoxville, TN. 6th and 27th of September 2023
    
    \item \textit{An Analysis of Vector-Borne Plant Disease Models Incorporating Vector-Induced Host Responses}
    \\
    Pacific Math Alliance - PUMP Research Symposium, California State University, Northridge, CA, 28 April 2018.
\end{etaremune}


\begin{center}
    \textbf{\underline{PROFESSIONAL MEMBERSHIPS}}
\end{center}
SIAM, AMS, MAA

\begin{center}
    \textbf{\underline{TECHNICAL SKILLS}}
\end{center}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item MATLAB - Proficient; used in many course projects, Master's Thesis research, and all throughout current research work for PhD Dissertation.
    \item R - Proficient with several packages utilized for statistical analysis, regression, some Markov Chain Monte Carlo.
    \item \LaTeX - Proficient; used to submit homework for courses since undergraduate studies, as well as assignments for teaching, technical reports, Master's Thesis, published/submitted works, and PhD Dissertation.
    \item Python - Some experience; mostly used for coursework during MS degree (CSUN).
    \item Mathematica - Some experience; mostly used for coursework during MS and PhD degree.
    \item Maple - Some experience; mostly used for Master's Thesis research.
    \item Microsoft Office - Proficient.
\end{itemize}

\vspace{16pt}

\begin{center}
    \textbf{\underline{SERVICE}}
\end{center}
\textbf{University of Tennessee, Knoxville} \hfill Knoxville, TN
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Mathematics Department Representative, Graduate Student Senate
  \hfill September 2019 $-$ August 2022
\\
    Committees: Fundraising, Graduate Student Mental Health and Wellbeing, GSS Travel Awards
    \item  Graduate Student Mentor (2 students)
  \hfill August 2020 $-$ May 2021
    \item Treasurer for UTK Chapter, Society for Advancement of Chicanos/Hispanics \& Native Americans in Science (SACNAS)
  \hfill August 2020 $-$ May 2021
\end{itemize}

\vspace{16pt}

% \begin{center}
%     \textbf{\underline{REFERENCES}}
% \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentor and mentees for Android and iOS platform.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}
